Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-06-19 WRITEUP/ms.tex
incoporated some DR comments, added source ID in intro, added ack section, fixed wrong peak separation and dynamical mass

\citestyle{aa}
\shorttitle{Molecular Gas in the Lensed Wet-Merger RXJ1131 at $z$\,=\,0.65}
\shortauthors{Leung \& Riechers}

@@

\begin{abstract}
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
We use a concordance $\Lambda$CDM cosmology throughout this paper, with parameters from the WMAP9 results:
$H_0$ = 70 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.27, and $\Omega_{\Lambda}$ = 0.7 \citep{Hinshaw13a}.

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations}
\subsection{PdBI \bco} % DONE
Observations of the \bco rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz)
toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$\,=\,0.658
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX001; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively. The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup providing
an effective bandwidth of 3.6 GHz and a spectral resolution of 10.0 MHz ($\sim$
21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration and 1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as the primary flux calibrator for C and D
array observations, respectively, yielding $\lesssim$15\% calibration accuracy.

The \ncode{gildas} package was used to reduce and analyze the visibility data
which are then imaged and deconvolved using the CLEAN algorithm with ``natural"
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$ = 1.451 mJy \kms
beam\pmOne over 10 MHz (21.5 \kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
is created by averaging over all the line-free channels. This
yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15

\subsection{CARMA \cco} %DONE
Observations of the \cco rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz)
were carried out under the D array configurations of the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers) on 2014 February 02 under terrible 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions. The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
visibility data.

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$60\degr. We thus conservatively estimate
a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat its line intensity with caution and ensure that any physical interpretation
of this system (and thus implications and conclusions of this paper) do not rely on this quantity.

The \ncode{miriad} package was used to calibrate the visibility data which are
then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA = 8\degr) for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$
over a channel width of 25 MHz. An rms noise of
$\sigma$ = 0.831 mJy beam\pmOne is reached by averaging over the
line-free channels.

\subsection{VLA} %DONE
Our analysis also use the archival data of the radio continuum obtained with the \vla (VLA; Program ID: AW741; PI: Wucknitz). Since the observations have not been described in any previous publications, 
we here describe their details as well as our calibration steps.

Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C$-$band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz in each sideband.
The nearby radio quasar 1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
primary flux calibrator, and 0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We use \ncode{aips} to calibrate the visibility data which
are then imaged and deconvolved using
the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0\farcs18) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

\section{HST astrometry} %DONE
We obtain {\it HST} images from the Hubble Legacy Archive with
a goal to understand the origins of the emission detected
in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
resolution as the reference coordinate frame to align the optical ($V$-band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. Such astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
errors, and beam size.

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results}
\subsection{\bco Emission} \label{sec:CO21} %DONE
We dynamically resolved the \bco line emission toward the background galaxies
at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.65370 $\pm$ 0.0005. A highly asymmetric double-horned line profile is
detected as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3$\pm$2.6 and 24.0$\pm$2.0 mJy, and a FWHM of
179$\pm$9 \kms and 255$\pm$28 \kms, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 220 \kms. The integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

\begin{figure}[tbph]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$=0.6537, which is approximately the line center
considering the asymmetry is as a result of differential lensing.
A more detailed discussion of differential lensing effect is presented in
\Sec{differential} and the magnification factors for various kinematic
components are listed in \Tab{model}.
 \label{fig:CO21spec}}
\end{figure}

% moment 0 map: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct the zeroth, first and second moment maps shown in \Fig{CO21mom}
using the $uv$-continuum subtracted data cube, over $\Delta v$$\sim$750 \kms.
The first and second moment maps are clipped at 3$\sigma$.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne in the intensity-integrated
map. The deconvolved source size is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66
and thus the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as 2D-Gaussian,
the fit recovers the line intensity enclosed within the emitting
region, we therefore take this as an estimate on the extent of the lensed
emission. On the other hand, if we assume the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein Ring'' and
the lensed knots (see \Fig{CO21mom}).

@@

The emission of the red component coincides with the Einstein Ring seen in the
optical image, with most of its apparent flux originating from the lensed arc
in the Southeast, whereas the blue component is predominately coming from
solely the lensed arc shown in \Fig{CO21mom}. To illustrate this, we show the
channel maps of 21.5\,\kms width and spatial spectra of 1\farcs5 resolution in
\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures
show that emission
is present to the West, peaking toward the lensing arc (black across in
\Fig{chanmap}) in the red wing, and shifts to the East with decreasing velocity
(blue wing).
This indicates extended emission in the source plane, where
emission from different kinematic components is separated by different amounts
relative to the caustics. One consequence of such is the observed asymmetric
line profile. A detailed analysis on differential lensing of \bco is presented
in \Sec{differential}.

\begin{figure*}[tbph]
\centering
\includegraphics[width=1.0\textwidth]{../Figures/co_channel_maps.eps}
\caption{
Channel maps of PdBI \bco toward RXJ1131 in 21.5\,\kms resolution.
Black crosses indicate the position of the lensed knots (AGN emission,
which correspond to components ABCD in C06). The central white-filled
star indicates the position of the foreground lensing galaxy (component G
in C06). Contours start and increment at steps of
$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
\end{figure*}

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.85\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
\caption{
\bco spectrum as a function of position, binned by 3 pixels in each
direction (1\farcs5). The spectra map covers an extent of $\sim$10"$\times$10"
centering on the pixel that corresponds to the lensing galaxy. The velocity
and flux density scales are denoted in the top right panel.
BLAH: DR would want the pixel coordinates replaced by arcsec offset from
center. \label{fig:spatialSpec}}
\end{figure*}

We place an upper limit on \rot[HNC]{2}{1} line emission at the red-shifted
frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of
$\sigma$ = 1.451mJy per channel beam\pmOne.
Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$
limit of 4.353 mJy \kms beam\pmOne.

@@

\subsection{\bco Kinematics} % DONE
A clear velocity gradient and an unusually high
velocity dispersion ($\gtrsim$400\,\kms) near the central region
is seen in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of this data, the exceedingly
high velocity dispersion hints
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content. A velocity gradient across the source plane in \Fig{model} is also
found in our lens model. This further supports the idea of a
kinematically-ordered galaxy, but its emission has been lensed differentially.
In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
bright quasar and is in the process of merging.
We will defer the discussion of its implications to \Sec{dynamics},
where we analyze the dynamics of the system in the source plane.

@@

\subsection{\cco Emission} % DONE
We detect resolved \cco line emission toward RXJ1131. The spectrum is shown in
\Fig{co32spec}, which seems to have a double-peak profile.
This is expected if RXJ1131 is truly a disk galaxy (see previous
sections). The high phase noise in the calibration leads to a low SNR
detection. We thus estimate the line intensity to be
35.7$\pm$ 21.9 Jy\,\kms by summing up fluxes over the
linewidth used to infer \bco line intensity ($\sim$700 \kms).

\begin{figure}[!Htbp]
\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted \bco line profile (dashed).
The velocity scale is with respect to $z$=0.6537, which corresponds to the
dynamical center of the \bco line. The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

Assuming the spatial extents between \bco and \cco are similar and therefore
a negligible differential lensing effect, the line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,T$_{\small \cco}$$/$T$_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
The high uncertainty is dominated by the uncertainties in the \cco line
intensity.

\subsection{Interferometric Continuum} %DONE
No 1.5\,mm continuum emission is detected at the position of \cco
down to a 3$\sigma$ limit of 2.49mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.

We detect PdBI 2\,mm continuum in \Fig{cont}. The integrated flux density is
1.2\pmm0.2 mJy, with a peak flux
$S_\nu$\,=\,800\pmm88\,\micron Jy\,beam\pmOne
centering on the lensing galaxy. A slightly extended emission is also seen
along the lensed arc. This suggests that the detected emission comes from
both the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in $uv$-plane to remove the unresolved
emission toward the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_\nu$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission toward
the background galaxy.

\begin{figure}[!htbp]
%\centering
\includegraphics[trim=12 27 0 0, clip, width=0.45\textwidth]{../Figures/F555W_ContPdBI.eps}
\includegraphics[trim=10 5 0 0, clip, width=0.475\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{Top: an overlay of the 2\,mm continuum emission on the optical image.
Bottom: VLA 5\,GHz continuum emission is overlaid on the optical image.
Contours in both images start and increment at steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne and
$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne in the left and right panel, respectively.
The central crosses indicate the centroid of the foreground galaxy,
as detected in the optical image. The synthesis beams are shown in the bottom left corner of each panel.
\label{fig:cont}}\vspace{0.51em}
\end{figure}

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc and their centroids
coincide with the optical emission from the quasar.
We extract the flux densities for the arc and the core in \Tab{photometry}.
We find a spectral index of $\alpha$\,=\,$-$0.024 for the foreground
galaxy and $\alpha$\,=\,$-$0.345 for the background galaxy by fitting a
power-law (S$_\nu \propto \nu^{\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.

>>>>

\citestyle{aa}
\shorttitle{Molecular Gas in the Lensed Wet-Merger RXJ1131-1231 at $z$\,=\,0.65}
\shortauthors{Leung \& Riechers}

@@

\begin{abstract}
We \bco observations with the \pdbi.
evidence for differential lensing. 
wet-merger, Dynamical lens modeling 
the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations. 
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}

In this paper, we explore the ISM properties of the quadruply imaged
quasar RXS J113151.62-123158 (hereafter RXJ1131) at
$z_\textrm{AGN}$\,$=$\,0.685, with an Einstein ring of size
1\farcs83 in radius. The foreground lensing
galaxy is an elliptical galaxy at $z_\textrm{L}$\,$=$\,0.295. The redshifts
are spectroscopically confirmed by \citet{Sluse03a}. 
A black hole mass estimate of M$_{\rm BH}$\,$<$\,2\E{8}\Msun 
is also reported based on X-ray observations \citep{Reis14a}.

This paper is structured as follows.
In \Sec{obs} and \Sec{HST}, we outline the details of the observations and data reduction process.
In \Sec{results}, we report the measurements of the CO lines and photometry from optical to radio wavelengths. 
In \Sec{anal}, we represent our dynamical lens modeling on the \bco data and the physical properties inferred for  RXJ1131.
In \Sec{diss}, we discuss the results and implications of this study in the context of molecular gas evolution in mergers and massive galaxies.
Finally, we summarize the main results of this study and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = 69.32 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.29, and
$\Omega_{\Lambda}$ = 0.71 \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco} % DONE
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,230.5379938 GHz; $\nu_{\rm obs}$\,=\,139.4\,GHz)
toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$\,=\,0.658
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX001; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively. The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup providing
an effective bandwidth of 3.6 GHz and a spectral resolution of 10.0 MHz ($\sim$
21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and 1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding $\lesssim$15\% calibration accuracy.

The \ncode{gildas} package was used to reduce and analyze the visibility data
which are then imaged and deconvolved using the CLEAN algorithm with ``natural"
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$\,=\,1.45\,mJy\,\kms
beam\pmOne over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
is created by averaging over all the 3.16\,GHz line-free channels. This
yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15

\subsection{CARMA \cco} %DONE
Observations of the \cco rotational line in RXJ1131
($\nu_{\rm rest}$\,=\,345.7959899\,GHz; $\nu_{\rm rest}$\,=\,209.1\,GHz)
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions. The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
visibility data.

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
% rms scatter over ~ 90 klambda
% max baseline of obs. is 145 m
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
%
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$60\degr over $\sim$135\,m.
%BLAH... more like 50%
We thus conservatively estimate
a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat its line intensity with caution and ensure that any physical interpretation
of this system does not rely on this quantity.

The \ncode{miriad} package was used to calibrate the visibility data which are
then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA\,=\,8\degr) for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$
over a channel width of 25\,MHz. An rms noise of
$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
line-free channels.

\subsection{VLA (Archival)} %DONE
Our analysis also uses archival data of the 5\,GHz
radio continuum obtained with the
Very Large Array (VLA; Program ID: AW741; PI: Wucknitz).
Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C$-$band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz in each sideband.
The nearby radio quasar 1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
primary flux calibrator, and 0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We use \ncode{aips} to calibrate the visibility data which
are then imaged and deconvolved using
the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0\farcs18) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

\section{HST astrometry} \label{sec:HST}
We obtained an {\it HST} image taken with the F555W filter ($V$-band)
using the ACS/Wide Field Camera from the
Hubble Legacy Archive\footnote{Based on observations
made with the NASA/ESA Hubble Space Telescope, and obtained from the Hubble
Legacy Archive, which is a collaboration between the Space Telescope Science
Institute (STScI/NASA), the Space Telescope European Coordinating Facility
(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}
with a goal to understand the origin of the emission detected
in our mm observations. The details of the observations can be found
in C06. We adopt the VLA 5\,GHz map of
$\sim$0\farcs5 resolution as the
reference coordinate frame to align the optical ($V$-band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. This astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
errors, and beam size.

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21} %DONE
We detected the \bco line emission toward the background galaxies
at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.65370\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 and 24.0\pmm2.0 mJy, and a FWHM of
179$\pm$9 \kms and 255\pmm28 \kms, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$=0.6537, which is approximately the line center
considering the asymmetry as a result of differential lensing.
A detailed discussion of this effect is presented in
\Sec{differential} and the magnification factors for various kinematic
components are listed in \Tab{model}.
 \label{fig:CO21spec}}
\end{figure}

% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct the zeroth moment map (\Fig{CO21mom}) and
the higher-order first and second moment maps (\Fig{CO21highO})
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms. The higher-order moment maps are created using
channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity-integrated map. The deconvolved source size FWHM
is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, we therefore take this as an estimate on the extent of the lensed
emission. On the other hand, if we assume the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein Ring'' and
the lensed knots (see \Fig{CO21mom}).

@@

The emission of the red component coincides with the Einstein Ring seen in the
optical image, with most of its apparent flux originating from the lensed arc
in the southeast, whereas the blue component is predominately coming from
solely the lensed arc shown in \Fig{CO21mom}. To illustrate this, we show the
channel maps of 21.5\,\kms width and spatial spectra of 1\farcs5 resolution in
\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures
show that emission
is present to the west, peaking toward the lensing arc (black crosses in
\Fig{chanmap}) in the red wing, and shifts to the east with decreasing velocity
(blue wing).
This indicates extended emission in the source plane, where
emission from different kinematic components is separated by different amounts
relative to the caustics, leading to the observed asymmetric
line profile. A detailed analysis on differential lensing of \bco is presented
in \Sec{differential}, where we present our lens model.

\begin{figure*}[!htbp]
\centering
\includegraphics[width=1.0\textwidth]{../Figures/co_channel_maps.eps}
\caption{
Channel maps of PdBI \bco toward RXJ1131 in 21.5\,\kms resolution.
Black crosses indicate the position of the lensed knots (AGN emission,
which correspond to components ABCD in C06). The central white-filled
star indicates the position of the foreground lensing galaxy (component G
in C06). Contours start and increment at steps of
$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
\end{figure*}

\begin{figure*}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
\caption{
\bco spectrum as a function of position, binned by 3 pixels in each
direction (1\farcs5).
The spectra map covers an extent of $\sim$10"$\times$10"
centering on the pixel that corresponds to the lensing galaxy.
Spatial offset in arcsec is denoted in top left corner of each panel.
The velocity and flux density scales are denoted in the top right panel.
\label{fig:spatialSpec}}
\end{figure*}

We also place an upper limit on \rot[HNC]{2}{1} line emission
in the foreground galaxy at $z\sim$0.295.
Assuming a typical line width of 300\,\kms, this corresponds to a 3$\sigma$
limit of 0.35\,mJy\,\kms\,beam\pmOne.

@@

\subsection{\bco Kinematics} % DONE
A clear velocity gradient and a high
velocity dispersion ($\gtrsim$400\,\kms) near the central region
is seen in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of this data, the exceedingly
high velocity dispersion may hint
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content. A velocity gradient across the source plane in \Fig{model} is also
found in our lens model. This further supports the idea of a
kinematically-ordered galaxy, but its emission has been lensed differentially.
In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
bright quasar and is in the process of merging.
We will defer the discussion of its implications to \Sec{dynamics},
where we analyze the dynamics of the system in the source plane.

@@

\subsection{\cco Emission} % DONE
We detect resolved \cco line emission toward RXJ1131. The spectrum is shown in
\Fig{co32spec}, which seems to have a double-peak profile.
This is expected if RXJ1131 is truly a disk galaxy (see previous
sections). The high phase noise in the calibration leads to a low SNR
detection. We thus estimate the line intensity to be
35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer \bco line intensity ($\sim$700 \kms).

\begin{figure}[!Htbp]
\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is with respect to $z$=0.6537, which corresponds to the
dynamical center of the \bco line. The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

Assuming the spatial extents between \bco and \cco are similar and therefore
a negligible differential lensing effect, the line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,T$_{\small \cco}$$/$T$_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.

\subsection{Continuum Emission} %DONE
No 1.5\,mm continuum emission is detected at the position of \cco
down to a 3$\sigma$ limit of 2.49\,mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.

We detect PdBI 2\,mm continuum in \Fig{cont}. The integrated flux density is
1.2\pmm0.2 mJy, with a peak flux
$S_\nu$\,=\,800\pmm88\,$\mu$Jy\,beam\pmOne
centering on the lensing galaxy. Slightly extended emission is also detected
along the lensed arc. This suggests that the detected emission comes from
both the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in $uv$-plane to remove the unresolved
emission toward the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_\nu$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission toward
the background galaxy.

\begin{figure}[!htbp]
%\centering
\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{../Figures/F555W_ContPdBI.eps}
\includegraphics[trim=13 5 0 0, clip, width=0.475\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{Top: an overlay of the 2\,mm continuum emission on the optical image.
Bottom: VLA 5\,GHz continuum emission is overlaid on the optical image.
Contours in both images start and increment at steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne and
$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne in the left and right panel, respectively.
The central crosses indicate the centroid of the foreground galaxy,
as detected in the optical image. The synthesis beams are shown in the bottom left corner of each panel.
\label{fig:cont}}\vspace{0.51em}
\end{figure}

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc and their centroids
coincide with the optical emission from the quasar.
We extract the flux densities for the arc and the core in \Tab{photometry}.
We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
for the foreground
galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
for the background galaxy by fitting a
power-law (S$_\nu \propto \nu^{\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.
